# Data sources

Describe the data sources: who is responsible for collecting the data? How is it collected? If there were a choice of options, explain how you chose.

Provide some basic information about the dataset: types of variables, number of records, etc.

Describe any issues / problems with the data, either known or that you discover.

(suggested: approximately 1 page)

## Dataset Overview
All data collected has been observed and analyzed between 1st January 2020 and 30th April 2022.

**Nota bene: Because cryptocurrency markets do not have set trading hours and do not close for holidays or weekends, we receive daily data from 12am to 11:59pm. The S&P500 and DJI, on the other hand, are only traded Monday through Friday during fixed market hours.**

## Data Sources:

```{=tex}
\begin{itemize}
\item Use a linear kernel. 
\item Perform cross validation on a grid of values $\epsilon=0.1, 0.2, \cdots, 1$ and cost$=0.1, 0.5, 1, 5, 10, 50, 100$ values ....
\item What is the loss used in the cross validation (CV)?
\item Plot the cross validation heat map.
\item Train a linear kernel support vector regression using the optimal parameters selected using CV.
\item Compute the train and test error.
\end{itemize}
```

### Cryptocurrency Daily Price 

```{=tex}
\begin{itemize}
\item Obtained from https://www.investing.com/ in a csv format.
\item Contains Volume, opening price, high, low for each crypto currency.
\end{itemize}
```


### S&P500 and Dow Jones Index daily Price and Volume

```{=tex}
\begin{itemize}
\item Scraped from NASDAQ using Quandl library. NASDAQ being the official marketplace for financial and economic data,was the most reliable and efficient source. 
\item Contains Volume, opening price, closing price, high, low for each index
\end{itemize}
```


### MarketCap Data of Popular Crypto Currencies

```{=tex}
\begin{itemize}
\item Obtained from https://www.coingecko.com/ - using the library geckor.
\item They were several sources of marketcap data, the most popular being coinmarketcap - however API calls were expensive and not freely available. Coinmarketcap is the one stop source for all crypto data, for paid/premium users. Coingecko is a close alternative but doesnt provide globalmarketcap data. 
\item Because of the price point, and the necessity of global market capitalization data for our analysis, I manually obtained global market capitalization data from coinmarketcap and rendered it into a csv file - which has been separately uploaded to the git repository.
\end{itemize}
```



### Twitter Data
```{=tex}
\begin{itemize}
\item The academicTwitter library is only available upon request to some users and the regular Twitter developer API doesnt provide historical data beyond 7 days. 
\item We tried scraping mentions on twitter per keyword, but each callback only allowed for 1500 tweets and limited us to 1 million tweets per day - which wouldnt have allowed us to obtain tweet_count by keyword for the last 2 years.
\item The data was finally obtained by scraping a publicly available graph  on bitinfocharts using python( added separately to git repository ) and the data was rendered into a csv file - which was then used to analyse count of tweets for the keywords - ethereum, dogecoin and bitcoin.
\end{itemize}
```



```{r library loading,message=FALSE,warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyquant)
library(skimr)
library(tidyverse)
library(Quandl)
library(lubridate)
library(dplyr)
library(ggplot2)
library(redav)
library(plotly)
library(reshape2)
library(geckor)
library(crypto2)
library(hrbrthemes)
#library("imputeTS")
library(coinmarketcapr)
library(hrbrthemes)
library(plyr)
library(treemap)
library(treemapify)





#coinmarketgecko api - https://www.coingecko.com/
#install.packages("geckor")
#install.packages("crypto2")
# install.packages("devtools")
# install.packages("coinmarketcapr")
# devtools::install_github("business-science/tidyquant")
# install.packages("skimr")
# remotes::install_github("jtr13/redav")

```

```{r data loading}

#2.1 Daily Price of 3 popular crypto currencies and 2 standard market indices -----------------------
tq_index("SP500")
sandp_hist_prices <- tq_get(c("^GSPC"),
              get = "stock.prices",
              from   = "2020-01-01",
              to     = "2022-04-30"
              )
dji_hist_prices <- tq_get(c("^DJI"),
                          get = "stock.prices",
                          from   = "2020-01-01",
                          to     = "2022-04-30"
                          )
# #historical crypto prices of 2 largest currencies by marketcap
# eth <- read.csv("https://raw.githubusercontent.com/nupurjoshii/StatGraphicsProject/main/prices_eth.csv", header = TRUE)
# btc <- read.csv("https://raw.githubusercontent.com/nupurjoshii/StatGraphicsProject/main/prices_btc.csv",header = TRUE)
# doge <- read.csv("https://raw.githubusercontent.com/nupurjoshii/StatGraphicsProject/main/prices_doge.csv",header = TRUE)

#2.2 MarketCap Data of Popular Crypto Currencies

#checking crypto list and sorting by volume
list <- crypto_list() %>%
  arrange(rank)
#list[order(list$rank , na.last = TRUE)]
#getting eth marketcap data
eth_history <- coin_history(coin_id = "ethereum", 
                            vs_currency = "usd",
                            days = 1000)
eth_history$date <- as.Date(eth_history$timestamp,format="%Y/%m/%d")
eth_v1 = subset(eth_history, select = -c(timestamp))
eth <- eth_v1 %>% filter(date >= '2020-01-01', date <= '2022-04-30')
#head(eth)

#getting btc marketcap data
btc_history <- coin_history(coin_id = "bitcoin", 
                            vs_currency = "usd",
                            days = 1000)
btc_history$date <- as.Date(btc_history$timestamp,format="%Y/%m/%d")
btc_v1 = subset(btc_history, select = -c(timestamp))
btc <- btc_v1 %>% filter(date >= '2020-01-01', date <= '2022-04-30')
#head(btc)

#getting doge marketcap data
doge_history <- coin_history(coin_id = "dogecoin", 
                            vs_currency = "usd",
                            days = 1000)
doge_history$date <- as.Date(doge_history$timestamp,format="%Y/%m/%d")
doge_v1 = subset(doge_history, select = -c(timestamp))
doge <- doge_v1 %>% filter(date >= '2020-01-01', date <= '2022-04-30')
#head(doge)

#getting cardano marketcap data
cardano_history <- coin_history(coin_id = "cardano", 
                             vs_currency = "usd",
                             days = 1000)
cardano_history$date <- as.Date(cardano_history$timestamp,format="%Y/%m/%d")
cardano_v1 = subset(cardano_history, select = -c(timestamp))
cardano <- cardano_v1 %>% filter(date >= '2020-01-01', date <= '2022-04-30')
#head(cardano)

#getting binance coin marketcap data
binancecoin_history <- coin_history(coin_id = "binancecoin", 
                                vs_currency = "usd",
                                days = 1000)
binancecoin_history$date <- as.Date(binancecoin_history$timestamp,format="%Y/%m/%d")
binancecoin_v1 = subset(binancecoin_history, select = -c(timestamp))
binancecoin <- binancecoin_v1 %>% filter(date >= '2020-01-01', date <= '2022-04-30')
#head(binancecoin)

# Look at distribution of twitter crypto mentions per crypto coin

#Twitter Data
#data scraped from bitinfocharts using python - python code uploaded separately
btc_tweet_count <- read.csv("https://raw.githubusercontent.com/nupurjoshii/StatGraphicsProject/main/btc_tweets.csv")
eth_tweet_count <- read.csv("https://raw.githubusercontent.com/nupurjoshii/StatGraphicsProject/main/eth_tweets.csv")
doge_tweet_count <- read.csv("https://raw.githubusercontent.com/nupurjoshii/StatGraphicsProject/main/doge_tweets.csv")

#Latest Global Market Cap Data as on 30th April 2022
crypto_total_value <- read.csv("https://raw.githubusercontent.com/nupurjoshii/StatGraphicsProject/main/Crypto_LatestMarketCap.csv")

```

