# Results

###Market Capitalization of cryptocurrencies 2020-2022
The value of the total cryptocurrency market has risen to more than 1.5 trillion, owing to the meteoric rise of bitcoin, ether, and dogecoin. With a market cap of approximately 67 billion, Dogecoin alone is worth more than 75% of the companies in the S&P 500. Although digital currencies have grown in popularity in recent months, they remain a small part of the global markets for stocks, bonds, and gdp.

### With great returns come great volatility
Much of the hype surrounding cryptocurrencies has been self-fulfilling. During the pandemic, trading volume increased as a growing number of investors gained access to crypto markets via a variety of platforms. Investors see incredible gains and enter the market, putting additional upward pressure on prices. However, every breathtaking rally has been followed by an equally punishing crash, and cryptocurrencies lack a fundamental anchor like the par value of a bond or the discounted cash flows of a stock.
Newer Entrants Are the Top Drivers of Cryptocurrency Growth
We weren't surprised to discover that bitcoin accounted for most of the growth of the cryptocurrency market in aggregate, but it was surprising to see that bitcoin has rapidly lost market share to these other cryptocurrencies in recent months. 
Ether accounts for the first leg of that lopsided growth. And though altcoins like cardano , binance coin and dogecoin are often overlooked, their market share has grown substantially over the past    months
Ether has experienced sharp spikes and tumbles in its price as enthusiasts speculated on a wide variety of applications for the ethereum blockchain like NFT.

###The Power of Social Media

The rise of dogecoin has defined the power of memes more than any other move in digital-currency markets. It is a cryptocurrency that was created as a joke but has since risen more than 10,000% by 2021. Dogecoin's total market value soared to more than $80 billion at its peak in 2021. Dogecoin's wild swings should serve as a cautionary note to bitcoin investors as well. While the early supporters of cryptocurrency emphasized its utility as an inflation hedge or a store of value, it has no long-term history as either, and its value is heavily influenced by sentiment and momentum. If sentiment turns against it, the price may fall, and a rising price is bitcoin's most appealing feature to new investors


## Crypto Work and Graphs

```{r crypto_work, warning=FALSE,message=FALSE}

# Price-Trends for Ethereum, Bitcoin and Doge

#ETH Chart
eth[which.max(eth$price),]
eth %>% 
  ggplot( aes(x= date, y= price)) +
  geom_line(color="#69b3a2") +
  ylim(0,5000) +
  annotate(geom="text", x=as.Date("2021-01-01"), y=4808, 
           label="Ethereum price reached 4.8k$\nat the end of 2021") +
  annotate(geom="point", x=as.Date("2021-11-08"), y=4808, size=8, shape=21, fill="transparent") +
  theme_ipsum()

#Bitcoin Chart
btc[which.max(btc$price),]
btc %>% 
  ggplot( aes(x= date, y= price)) +
  geom_line(color="#69b3a2") +
  ylim(0,70000) +
  annotate(geom="text", x=as.Date("2020-11-07"), y=67000 ,
           label="Bitcoin price reached 67.5k$\nat the end of 2021") +
  annotate(geom="point", x=as.Date("2021-11-07"), y=67527.9, size=8, shape=21, fill="transparent") +
  theme_ipsum()


#Doge Chart
doge[which.max(doge$price),]
doge %>% 
  ggplot( aes(x= date, y= price)) +
  geom_line(color="#69b3a2") +
  ylim(0,0.8) +
  annotate(geom="text", x=as.Date("2020-08-07"), y=0.69, 
           label="Doge price reached an all time high\non 7th May 2021. \nElon Musk appeared on SNL on 8th May 2021") +
  annotate(geom="point", x=as.Date("2021-05-07"), y=0.69, size=8, shape=21, fill="transparent") +
  theme_ipsum()

combined_cryptos <-rbind(eth,btc,doge,cardano,binancecoin) %>%
  group_by(coin_id) %>% 
  mutate(index = 100*price/price[1],
         pc_change = 100*(price- lag(price))/lag(price)) %>%
  ungroup()
  

p1 <-plot_ly(combined_cryptos, x = ~date, y = ~index, color = ~coin_id, title = "Index") %>%
  add_lines() %>%
  layout(yaxis = list(title = "Index"))
# 
p2 <- plot_ly(combined_cryptos, x = ~date, y = ~pc_change, color = ~coin_id, title = "Percent Change") %>%
  add_lines() %>%
  layout(yaxis = list(title = "Daily Percent Change"))
# 
p3 <- plot_ly(combined_cryptos, x = ~date, y = ~price, color = ~coin_id, title = "Price") %>% 
  add_lines() %>%
  layout(yaxis = list(title = "Price($)"))

subplot(style(p1, showlegend = FALSE),
        style(p2, showlegend = FALSE),
        style(p3, showlegend = TRUE),
        titleY = TRUE,
        margin = 0.05) %>%
  layout(title = "Crypto Market Over Time")

# Make Boxplot of Cryptos pc_change --> Distribution of daily percentage change of cryptos

plot_ly(combined_cryptos, x = ~pc_change, color = ~coin_id, type = "box") %>%
  layout(title = "Crypto Market:Box Plot Distribution of Daily Percentage Change",
         xaxis = list(title = "Daily Percentage Change"), margin = 0.02)



```
## Stock Graphs

```{r stockgraphs}
stock_indices <- rbind(dji_hist_prices, sandp_hist_prices) %>%
  mutate(symbol = if_else(symbol == "^GSPC", "S & P 500", "Dow Jones")) %>%
  group_by(symbol) %>% 
  mutate(index = 100*close/close[1],
         daily_pc_change = 100*(close- lag(close))/lag(close)) %>%
  ungroup()


P1 <-plot_ly(stock_indices, x = ~date, y = ~index, color = ~symbol) %>%
  add_lines() %>%
  layout(yaxis = list(title = "Relative Index"))
# 
P2 <- plot_ly(stock_indices, x = ~date, y = ~daily_pc_change, color = ~symbol) %>%
  add_lines() %>%
  layout(yaxis = list(title = "Daily Percent Change"))
# 
P3 <- plot_ly(stock_indices, x = ~date, y = ~close, color = ~symbol) %>% 
  add_lines() %>%
  layout(yaxis = list(title = "Index Value"))

subplot(style(P1, showlegend = FALSE),
        style(P2, showlegend = FALSE),
        style(P3, showlegend = TRUE),
        titleY = TRUE,
        margin = 0.05) %>%
  layout(title = "Stock Market Over Time")

# Make Boxplot of DJI vs SP500 daily pc_change

plot_ly(stock_indices, x = ~daily_pc_change, color = ~symbol, type = "box") %>% 
  layout(title = "Stock Market: Box Plot Distribution of Daily Percentage Change",
         xaxis = list(title = "Daily Percentage Change"), margin = 0.02)

#S&P Chart

fig <- sandp_hist_prices %>% plot_ly(x = ~date, type="candlestick",
                      open = ~sandp_hist_prices$open, close = ~sandp_hist_prices$close,
                      high = ~sandp_hist_prices$high, low = ~sandp_hist_prices$low) 
fig <- fig %>% layout(title = "S$P500 Price-Trend")

fig


#DJI Chart

fig2 <- dji_hist_prices %>% plot_ly(x = ~date, type="candlestick",
                                     open = ~dji_hist_prices$open, close = ~dji_hist_prices$close,
                                     high = ~dji_hist_prices$high, low = ~dji_hist_prices$low) 
fig2 <- fig2 %>% layout(title = "DJI Price-Trend")

fig2

```

## Heatmap Price

```{r}

# Correlation HeatMap

btc_price_column <- btc %>%
  dplyr::select(price) %>%
  mutate(Bitcoin = price) %>%
  select(Bitcoin)

eth_price_column <- eth %>%
  dplyr::select(price) %>%
  mutate(Ethereum = price) %>%
  select(Ethereum)

doge_price_column <- doge %>%
  dplyr::select(price) %>%
  mutate(Dogecoin = price) %>%
  select(Dogecoin)

cardano_price_column <- cardano %>%
  dplyr::select(price) %>%
  mutate(Cardano = price) %>%
  select(Cardano)

binancecoin_price_column <- binancecoin %>%
  dplyr::select(price) %>%
  mutate(Binancecoin = price) %>%
  select(Binancecoin)

cryptos_price_list <- cbind(btc_price_column, eth_price_column, doge_price_column, cardano_price_column, binancecoin_price_column, btc$date)

corr_cryptos <- cryptos_price_list %>%
  dplyr::select(-`btc$date`) %>% 
  cor()

corr_cryptos <- round(corr_cryptos, 3)

# Following Code was copied from the example found here:
# http://www.sthda.com/english/wiki/ggplot2-quick-correlation-matrix-heatmap-r-software-and-data-visualization

cormat <-corr_cryptos


melted_corr_cryptos <- melt(corr_cryptos)


# Get lower triangle of the correlation matrix
  get_lower_tri<-function(cormat){
    cormat[upper.tri(cormat)] <- NA
    return(cormat)
  }
  # Get upper triangle of the correlation matrix
  get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
  }
  
reorder_cormat <- function(cormat){
# Use correlation between variables as distance
dd <- as.dist((1-cormat)/2)
hc <- hclust(dd)
cormat <-cormat[hc$order, hc$order]
}
  
  
# Reorder the correlation matrix
cormat <- reorder_cormat(cormat)
upper_tri <- get_upper_tri(cormat)
# Melt the correlation matrix
melted_cormat <- melt(upper_tri, na.rm = TRUE)
# Create a ggheatmap
ggheatmap_price <- ggplot(melted_cormat, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
    name="Pearson\nCorrelation") +
  theme_minimal()+ # minimal theme
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 12, hjust = 1))+
 coord_fixed()

price_heatmap <- ggheatmap_price + 
geom_text(aes(Var2, Var1, label = value), color = "black", size = 4) +
theme(
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  panel.grid.major = element_blank(),
  panel.border = element_blank(),
  panel.background = element_blank(),
  axis.ticks = element_blank(),
  legend.justification = c(1, 0),
  legend.position = c(1.5, 0),
  legend.direction = "vertical")+
  guides(fill = guide_colorbar(barwidth = 1, barheight = 10,
                title.position = "top", title.hjust = 0.5))

price_heatmap + labs(title = "Correlation Heatmap: Cryptocurrency Prices",
                     subtitle = "The price movement of most of these are very highly correlated.")


```

## Heatmap Percent Change
```{r pc-change_heatmap}

# Repeat the Process for PC change

# Correlation HeatMap

btc_pchange_column <- btc %>%
  mutate(index = 100*price/price[1],
         pc_change = 100*(price- lag(price))/lag(price)) %>% 
  dplyr::select(pc_change) %>%
  mutate(Bitcoin = pc_change) %>%
  select(Bitcoin)

eth_pchange_column <- eth %>%
  mutate(index = 100*price/price[1],
           pc_change = 100*(price- lag(price))/lag(price)) %>%
  dplyr::select(pc_change) %>%
  mutate(Ethereum = pc_change) %>%
  select(Ethereum)

doge_pchange_column <- doge %>%
  mutate(index = 100*price/price[1],
         pc_change = 100*(price- lag(price))/lag(price)) %>%
  dplyr::select(pc_change) %>%
  mutate(Dogecoin = pc_change) %>%
  select(Dogecoin)

cardano_pchange_column <- cardano %>%
  mutate(index = 100*price/price[1],
         pc_change = 100*(price- lag(price))/lag(price)) %>%
  dplyr::select(pc_change) %>%
  mutate(Cardano = pc_change) %>%
  select(Cardano)

binancecoin_pchange_column <- binancecoin %>%
  mutate(index = 100*price/price[1],
         pc_change = 100*(price- lag(price))/lag(price)) %>%
  dplyr::select(pc_change) %>%
  mutate(Binancecoin = pc_change) %>%
  select(Binancecoin)

cryptos_pchange_list <- cbind(btc_pchange_column, eth_pchange_column, doge_pchange_column, cardano_pchange_column, binancecoin_pchange_column, btc$date) %>%
  drop_na()


sandp_pchange_column <- sandp_hist_prices %>%
  mutate(index = 100*close/close[1],
           pc_change = 100*(close- lag(close))/lag(close)) %>%
  dplyr::select(pc_change,date) %>%
  dplyr::rename(`S & P 500` = pc_change)

dowjones_pchange_column <- dji_hist_prices %>%
  mutate(index = 100*close/close[1],
           pc_change = 100*(close- lag(close))/lag(close)) %>%
  dplyr::select(pc_change,date) %>%
  dplyr::rename(`Dow Jones` = pc_change)

stocks_pchange_list <- left_join(sandp_pchange_column, dowjones_pchange_column)

cryptos_stocks_pchange_list <- left_join(cryptos_pchange_list, stocks_pchange_list, by = c("btc$date" = "date"))

corr_cryptos_pchange <- cryptos_pchange_list %>%
  dplyr::select(-`btc$date`) %>% 
  cor()

corr_cryptos_stocks_pchange <- cryptos_stocks_pchange_list %>%
  dplyr::select(-`btc$date`) %>% 
  drop_na() %>% 
  cor()

corr_cryptos_pchange <- round(corr_cryptos_pchange, 3)

corr_cryptos_stocks_pchange <- round(corr_cryptos_stocks_pchange, 3)

# Following Code was copied from the example found here:
# http://www.sthda.com/english/wiki/ggplot2-quick-correlation-matrix-heatmap-r-software-and-data-visualization

#cormat <-corr_cryptos_pchange

cormat <- corr_cryptos_stocks_pchange



melted_corr_cryptos_stocks <- melt(corr_cryptos_stocks_pchange)

melted_cormat <- melted_corr_cryptos


# Get lower triangle of the correlation matrix
  get_lower_tri<-function(cormat){
    cormat[upper.tri(cormat)] <- NA
    return(cormat)
  }
  # Get upper triangle of the correlation matrix
  get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
  }
  
reorder_cormat <- function(cormat){
# Use correlation between variables as distance
dd <- as.dist((1-cormat)/2)
hc <- hclust(dd)
cormat <-cormat[hc$order, hc$order]
}
  
  
# Reorder the correlation matrix
cormat <- reorder_cormat(cormat)
upper_tri <- get_upper_tri(cormat)
# Melt the correlation matrix
melted_cormat <- melt(upper_tri, na.rm = TRUE)
# Create a ggheatmap
ggheatmap_pchange <- ggplot(melted_cormat, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
    name="Pearson\nCorrelation") +
  theme_minimal()+ # minimal theme
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 12, hjust = 1))+
 coord_fixed()


pchange_heatmap <- ggheatmap_pchange + 
geom_text(aes(Var2, Var1, label = value), color = "black", size = 4) +
theme(
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  panel.grid.major = element_blank(),
  panel.border = element_blank(),
  panel.background = element_blank(),
  axis.ticks = element_blank(),
  legend.justification = c(1, 0),
  legend.position = c(1.5, 0),
  legend.direction = "vertical")+
  guides(fill = guide_colorbar(barwidth = 1, barheight = 10,
                title.position = "top", title.hjust = 0.5))

pchange_heatmap + labs(title = "Correlation Heatmap:Crypto and Stocks Daily % Change",
                     subtitle = "Dogecoin and Stocks correlation values stick out.")
```

## Index Heatmap

```{r index_heatmap}

# Repeat the Process for Index Method

# Correlation HeatMap

btc_index_column <- btc %>%
  mutate(index = 100*price/price[1],
         pc_change = 100*(price- lag(price))/lag(price)) %>% 
  dplyr::select(index) %>%
  dplyr::rename(Bitcoin = index)

eth_index_column <- eth %>%
  mutate(index = 100*price/price[1],
           pc_change = 100*(price- lag(price))/lag(price)) %>%
  dplyr::select(index) %>%
  dplyr::rename(Ethereum = index)

doge_index_column <- doge %>%
  mutate(index = 100*price/price[1],
         pc_change = 100*(price- lag(price))/lag(price)) %>%
  dplyr::select(index) %>%
  dplyr::rename(Dogecoin = index)

cardano_index_column <- cardano %>%
  mutate(index = 100*price/price[1],
         pc_change = 100*(price- lag(price))/lag(price)) %>%
  dplyr::select(index) %>%
  dplyr::rename(Cardano = index)

binancecoin_index_column <- binancecoin %>%
  mutate(index = 100*price/price[1],
         pc_change = 100*(price- lag(price))/lag(price)) %>%
  dplyr::select(index) %>%
  dplyr::rename(Binancecoin = index)


cryptos_index_list <- cbind(btc_index_column, eth_index_column, doge_index_column, cardano_index_column, binancecoin_index_column, btc$date) %>%
  drop_na()

sandp_index_column <- sandp_hist_prices %>%
  mutate(index = 100*close/close[1],
           pc_change = 100*(close- lag(close))/lag(close)) %>%
  dplyr::select(index,date) %>%
  dplyr::rename(`S & P 500` = index)

dowjones_index_column <- dji_hist_prices %>%
  mutate(index = 100*close/close[1],
           pc_change = 100*(close- lag(close))/lag(close)) %>%
  dplyr::select(index,date) %>%
  dplyr::rename(`Dow Jones` = index)

stocks_index_list <- left_join(sandp_index_column, dowjones_index_column)

cryptos_stocks_index_list <- left_join(cryptos_index_list, stocks_index_list, by = c("btc$date" = "date"))



corr_cryptos_stocks_index <- cryptos_stocks_index_list %>%
  dplyr::select(-`btc$date`) %>% 
  drop_na() %>% 
  cor()


corr_cryptos_stocks_index <- round(corr_cryptos_stocks_index, 3)

# Following Code was copied from the example found here:
# http://www.sthda.com/english/wiki/ggplot2-quick-correlation-matrix-heatmap-r-software-and-data-visualization

#cormat <-corr_cryptos_pchange

cormat <- corr_cryptos_stocks_index

melted_corr_cryptos_stocks <- melt(corr_cryptos_stocks_index)

melted_cormat <- melted_corr_cryptos

# Get lower triangle of the correlation matrix
  get_lower_tri<-function(cormat){
    cormat[upper.tri(cormat)] <- NA
    return(cormat)
  }
  # Get upper triangle of the correlation matrix
  get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
  }
  
reorder_cormat <- function(cormat){
# Use correlation between variables as distance
dd <- as.dist((1-cormat)/2)
hc <- hclust(dd)
cormat <-cormat[hc$order, hc$order]
}
  
  
# Reorder the correlation matrix
cormat <- reorder_cormat(cormat)
upper_tri <- get_upper_tri(cormat)
# Melt the correlation matrix
melted_cormat <- melt(upper_tri, na.rm = TRUE)
# Create a ggheatmap
ggheatmap_index <- ggplot(melted_cormat, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
    name="Pearson\nCorrelation") +
  theme_minimal()+ # minimal theme
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 12, hjust = 1))+
 coord_fixed()


index_heatmap <- ggheatmap_index + 
geom_text(aes(Var2, Var1, label = value), color = "black", size = 4) +
theme(
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  panel.grid.major = element_blank(),
  panel.border = element_blank(),
  panel.background = element_blank(),
  axis.ticks = element_blank(),
  legend.justification = c(1, 0),
  legend.position = c(1.25, 0),
  legend.direction = "vertical")+
  guides(fill = guide_colorbar(barwidth = 1, barheight = 10,
                title.position = "top", title.hjust = 0.5))

index_heatmap +labs(title = "Correlation Heatmap: Crypto and Stocks Relative Indices",
                     subtitle = "Very high values across; Dogecoin lowest of bunch.")
```

## Twitter

```{r twitter}
btc_eth_doge_tweets <- rbind(btc_tweets,eth_tweets,doge_tweets)

plot_ly(btc_eth_doge_tweets, x = ~Date, y = ~TweetCount, color = ~symbol) %>% add_lines %>%
  layout(title = "Cryptocurrency Daily Tweet Frequency",
         yaxis = list(title = " Daily Tweet Frequency"),
         margin = 0.01)


```

## Twitter Correlation Heatmap

```{r}
btc_tweets_column <- btc_tweets %>%
  mutate(pc_TweetCount = 100*(TweetCount- lag(TweetCount))/lag(TweetCount)) %>% 
  dplyr::select(pc_TweetCount) %>%
  dplyr::rename(`Bitcoin Tweets` = pc_TweetCount)

eth_tweets_column <- eth_tweets %>%
  mutate(pc_TweetCount = 100*(TweetCount- lag(TweetCount))/lag(TweetCount)) %>% 
  dplyr::select(pc_TweetCount) %>%
  dplyr::rename(`Ethereum Tweets` = pc_TweetCount)

doge_tweets_column <- doge_tweets %>%
  mutate(pc_TweetCount = 100*(TweetCount- lag(TweetCount))/lag(TweetCount)) %>% 
  dplyr::select(pc_TweetCount) %>%
  dplyr::rename(`Dogecoin Tweets` = pc_TweetCount)

# Correlation HeatMap

btc_pchange_column <- btc %>%
  mutate(index = 100*price/price[1],
         pc_change = 100*(price- lag(price))/lag(price)) %>% 
  dplyr::select(pc_change) %>%
  dplyr::rename(Bitcoin = pc_change)

eth_pchange_column <- eth %>%
  mutate(index = 100*price/price[1],
           pc_change = 100*(price- lag(price))/lag(price)) %>%
  dplyr::select(pc_change) %>%
  dplyr::rename(Ethereum = pc_change)

doge_pchange_column <- doge %>%
  mutate(index = 100*price/price[1],
         pc_change = 100*(price- lag(price))/lag(price)) %>%
  dplyr::select(pc_change) %>%
  dplyr::rename(Dogecoin = pc_change)

cryptos_pchange_tweets_list <- cbind(btc_pchange_column, eth_pchange_column, doge_pchange_column,
                                     btc_tweets_column, eth_tweets_column, doge_tweets_column,
                                     btc$date) %>%
  drop_na()


sandp_pchange_column <- sandp_hist_prices %>%
  mutate(index = 100*close/close[1],
           pc_change = 100*(close- lag(close))/lag(close)) %>%
  dplyr::select(pc_change,date) %>%
  dplyr::rename(`S & P 500` = pc_change)

dowjones_pchange_column <- dji_hist_prices %>%
  mutate(index = 100*close/close[1],
           pc_change = 100*(close- lag(close))/lag(close)) %>%
  dplyr::select(pc_change,date) %>%
  dplyr::rename(`Dow Jones` = pc_change)

stocks_pchange_list <- left_join(sandp_pchange_column, dowjones_pchange_column)

#cryptos_stocks_tweets_pchange_list <- left_join(cryptos_pchange_tweets_list, stocks_pchange_list,
                                                #by = c("btc$date" = "date"))

# IF interesting in studying crypto tweets to S&P and DJI, comment out bottom code and uncomment top one.

cryptos_stocks_tweets_pchange_list <- cryptos_pchange_tweets_list

corr_cryptos_pchange <- cryptos_pchange_list %>%
  dplyr::select(-`btc$date`) %>% 
  cor()

corr_cryptos_stocks_tweets_pchange <- cryptos_stocks_tweets_pchange_list %>%
  dplyr::select(-`btc$date`) %>% 
  drop_na() %>% 
  cor()

corr_cryptos_pchange <- round(corr_cryptos_pchange, 3)

corr_cryptos_stocks_tweets_pchange <- round(corr_cryptos_stocks_tweets_pchange, 3)

# Following Code was copied from the example found here:
# http://www.sthda.com/english/wiki/ggplot2-quick-correlation-matrix-heatmap-r-software-and-data-visualization

#cormat <-corr_cryptos_pchange

cormat <- corr_cryptos_stocks_tweets_pchange


melted_corr_cryptos_stocks_tweets <- melt(corr_cryptos_stocks_tweets_pchange)

melted_cormat <- melted_corr_cryptos_stocks_tweets


# Get lower triangle of the correlation matrix
  get_lower_tri<-function(cormat){
    cormat[upper.tri(cormat)] <- NA
    return(cormat)
  }
  # Get upper triangle of the correlation matrix
  get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
  }
  
reorder_cormat <- function(cormat){
# Use correlation between variables as distance
dd <- as.dist((1-cormat)/2)
hc <- hclust(dd)
cormat <-cormat[hc$order, hc$order]
}
  
  
# Reorder the correlation matrix
cormat <- reorder_cormat(cormat)
upper_tri <- get_upper_tri(cormat)
# Melt the correlation matrix
melted_cormat <- melt(upper_tri, na.rm = TRUE)
# Create a ggheatmap
ggheatmap_pchange_tweets <- ggplot(melted_cormat, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
    name="Pearson\nCorrelation") +
  theme_minimal()+ # minimal theme
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 12, hjust = 1))+
 coord_fixed()


pchange_tweets_heatmap <- ggheatmap_pchange_tweets + 
geom_text(aes(Var2, Var1, label = value), color = "black", size = 4) +
theme(
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  panel.grid.major = element_blank(),
  panel.border = element_blank(),
  panel.background = element_blank(),
  axis.ticks = element_blank(),
  legend.justification = c(1, 0),
  legend.position = c(1.5, 0),
  legend.direction = "vertical")+
  guides(fill = guide_colorbar(barwidth = 1, barheight = 10,
                title.position = "top", title.hjust = 0.5))

pchange_tweets_heatmap +
  labs(title = "Correlation Heatmap: Tweets vs Daily % Change",
       subtitle = "No significant correlation apparent.")

```



## Treemap
```{r treemap}

#Crypto in Context
#summarize values for tree map
CryptoCurrency <- c(crypto_total_value$Cryptocurrency[1:4])
MarketCap <- c(crypto_total_value$MarketCap[1:4])
rest <- sum(crypto_total_value$MarketCap, na.rm = FALSE) - sum(MarketCap)
df1 <- c(CryptoCurrency, 'Other')
df2 <- c(MarketCap, rest)

df <- data.frame( df1, df2)
df
ggplot(df, aes(area = df2, fill = df1, label = df1)) +
  geom_treemap() +
  geom_treemap_text(colour = "white",
                    place = "centre",
                    size = 11) +
  scale_fill_brewer(df2, palette = "Purples")
#change scale to value and not by alphabet

Markets <- c('CryptoCurrency', 'S&P', 'Bonds', 'Gold')
crypto_market_cap_global = sum(crypto_total_value$MarketCap)
s_p_market_cap_global = 3829000000 
bonds_market_cap_global = 11870000
gold_market_cap_global = 119000000
df2 <- c(crypto_market_cap_global,
         s_p_market_cap_global,
         bonds_market_cap_global,
         gold_market_cap_global)
df3 <- data.frame(Markets, df2)
#please make this better
ggplot(df3, aes(area = df2, fill = Markets, label = Markets)) +
  geom_treemap() +
  geom_treemap_text(colour = "white",
                    place = "centre",
                    size = 11) +
  scale_fill_brewer(df2, palette = "Greens")


#S&P marketcap source - Factset(S&P500)
#Gold marketcap source - https://companiesmarketcap.com/gold/marketcap/#:~:text=Estimated%20Market%20Cap%3A%20%2412.109%20T
#Bonds marketcap source - International Capital Markets Association
```

